Put Title here

### 2018-11-19 General WLD combinatorics.tex
maybe the small config result is correct now

\note{Are the next few definitions used outside the proof of Lemma~\ref{lem sian}?  If not, then perhaps they could go inside the proof so as not to clutter the document with temporary definitions?}
\begin{dfn}
Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$.  Denote this diagram by $W_{[i,j]}$.
\end{dfn}
\note{I think there's an issue here about what we mean by subdiagram; in def 1.5 we say a subdiagram is of the form $(P, V(P))$ which is certainly not what we want here; in fact I think we want the subdiagram where the vertex set is unchanged and only the propagator set is restricted (the other possibility would be to restrict the vertex set to $[i, j]$, but then the lengths of propagators can change and in the way we want to use it (see paragraph below) $p$ will become very non-admissible).  I think def 1.5 should be removed and we should say that for a WLD $(P, V)$ subdiagrams are any $(P', V')$ with $P'\subseteq P$, $V'\subseteq V$ and all supporting vertices of elements of $P'$ in $V'$; this seems to me to be the natural notion of subobject.}

@@

\begin{lem}\label{lem sian}
  Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
    \item $W$ admits no propagators of length 3, and one or both of the following two things occurs.
      \begin{enumerate}
        \item There is a propagator of length $2$, say $(i, i+1, i+2, i+3)$ such that no other propagators ends on either the edge $(i, i+1)$ or the edge $(i+2, i+3)$.\label{item lonely 2}
        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(i+2, i+3, i+4, i+5)$, and no other propagator ends on the edge $(i+2, i+3)$.\label{item pair of 2s}
      \end{enumerate}
  \end{enumerate}
\end{lem}

\begin{proof}
  Suppose first that $W$ has a propagator of length $3$, $p=(i, i+1, i+3, i+4)$.  By Remark~\ref{rm:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+1$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.

@@

  We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item lonely 2} or \ref{item pair of 2s} from the statement
  %a configuration \eqref{eq:2 prop config} in $D$
  or there is a propagator $q_r$ satisfying
\begin{itemize}
\item $\ell(q_r) \geq 4$.
\item $q_r$ bounds a region of $D$ which contains strictly fewer vertices than that bounded by $q_{r-1}$ and the restriction of $D$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
\end{itemize}
Since $D$ contains finitely many vertices, this must eventually terminate in one of the two desired configurations. %a configuration of the form \eqref{eq:2 prop config}.

Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+1,j_1+2,j_1+3)$ for its support.  If it is part of one of the two configurations we are looking for then we are done, 
%a configuration \eqref{eq:2 prop config} we are done,
so suppose otherwise: since $p_1$ is not in configuration \ref{item lonely 2} then there must be a second propagator starting either on edge $(j_1, j_1+1)$ or $(j_1+2, j_1+3)$.  Flipping the diagram if necessary, assume the former.  Since $p_1$ is not in configuration \ref{item pair of 2s} then there must exist a second propagator $q_1$ of length $\geq 4$ which starts on edge $(j_1,j_1+1)$.  This bounds a region $[i_1,j_1+1]$ which does not contain $p_1$.

Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,j_r+1]$.  Consider the restricted diagram $W_r:=W_{[i_r,j_r+1]}$; clearly we must have $s_l \geq 2$ for all $l \in [i_r+2,j_r-1]$ (which is a non-empty interval since $\ell(q_r) \geq 4$), while $s_l\geq 1$ for $l \in \{i_r,i_r+1,j_r,j_r+1\}$.

By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2 and none of length 3.  Let $p_{r+1}$ be a propagator of length 2 in $D_r$; if it forms part of either configuration \ref{item lonely 2} or \ref{item pair of 2s} 
%the configuration \eqref{eq:2 prop config}
then we are done.  Otherwise, at least one endpoint of $p_{r+1}$ lies on an edge contained in the non-empty interval $[i_r+2,j_r-1]$, and so there is at least one other propagator connected to this edge.  Up to symmetry, there are three possibilities:

% this was 100% a productive use of my time

\[\begin{tabular}{ccc}
% possibility 1
\begin{tikzpicture}
\pgfmathsetmacro{\radius}{2}
\pgfmathsetmacro{\angle}{15}
\begin{scope}
\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);

% vertices 
\foreach \i in {2,3,4,6,7,8,9,10}{
	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
}

% \dots 
\foreach \i in {1,2,3}{
	\node at (65 + \i*5:\radius cm) {$\cdot$};
}

\begin{scope} % this scope contains the propagators
\clip (0,0) circle[radius=\radius];

\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.7:\radius*1.2 cm); % q_r
\draw[propagator] (\angle*7.7:\radius*1.1 cm) to [bend left=90] (\angle*9.45:\radius*1.1 cm); % p_{r+1}

% grey prop begins here

\begin{scope}
\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.45cm];
\draw[light-gray,propagator,seconddash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
\end{scope}

\begin{scope}
\clip (0,0) circle[radius=\radius];
\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.4cm];
\draw[light-gray,propagator,firstdash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
\end{scope}

\begin{scope}
\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.3cm];
\clip (0,0) circle[radius=\radius];
\draw[light-gray,propagator] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
\end{scope}
% end gray prop

\end{scope}

\node at (90:\radius*0.30 cm) {\tiny $q_r$};
\node at (\angle*8:\radius*0.73) {\tiny $p_{r+1}$};
\node[light-gray] at (\angle*4.9:\radius*0.77 cm) {\tiny $q_{r+1}$};
\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
\node at (9*\angle:\radius*1.1) {\tiny $j_r$};

% circle/edges; needs to happen last to overlap gray
\begin{scope}
\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
\draw[-] (0,0) circle[radius=\radius cm];
\end{scope}

\end{scope} % ends the overall rectangle clipping
\end{tikzpicture}

&

% possibility 2
\begin{tikzpicture}
\pgfmathsetmacro{\radius}{2}
\pgfmathsetmacro{\angle}{15}
\begin{scope}
% overall clipping to make the size sensible
\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);

% vertices
\foreach \i in {2,3,4,6,7,8,9,10}{
	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
}

% \dots
\foreach \i in {1,2,3}{
	\node at (65 + \i*5:\radius cm) {$\cdot$};
}

\begin{scope} % props
\clip (0,0) circle[radius=\radius cm]; 
\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.6:\radius*1.2 cm); % q_r
\draw[propagator] (\angle*6.7:\radius*1.1 cm) to [bend left=90] (\angle*8.6:\radius*1.1 cm); % p_{r+1}

%% grey prop starts here

\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
\draw[light-gray,propagator,seconddash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
\end{scope}

\begin{scope}
\clip (0,0) circle[radius=\radius];
\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
\draw[light-gray,propagator,firstdash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
\end{scope}

\begin{scope}
\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
\clip (0,0) circle[radius=\radius];
\draw[light-gray,propagator] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
\end{scope}
% grey prop ends here

\node at (90:\radius*0.32 cm) {\tiny $q_r$};
\node at (\angle*7.75:\radius*0.75) {\tiny $p_{r+1}$};
\node[light-gray] at (\angle*4.5:\radius*0.7 cm) {\tiny $q_{r+1}$};
\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
\node at (9*\angle:\radius*1.1) {\tiny $j_r$};

% circle/edges
\begin{scope}
\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
\draw[-] (0,0) circle[radius=\radius cm];
\end{scope}

\end{scope} % ends overall clip
\end{tikzpicture}

&

% possiblitiy 3
\begin{tikzpicture}
\pgfmathsetmacro{\radius}{2}
\pgfmathsetmacro{\angle}{12}
\begin{scope}
\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);

% vertices
\foreach \i in {2,3,6,7,8,9,12,13}{
	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
}

% \dots
\foreach \i in {1,2,3}{
	\node at (44 + \i*5:\radius cm) {$\cdot$};
	\node at (116 + \i*5:\radius cm) {$\cdot$};
}

\begin{scope} % props
\clip (0,0) circle[radius=\radius cm];
\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*12.6:\radius*1.2 cm); % q_r
\draw[propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=100] (\angle*8.5:\radius*1.05 cm); % p_{r+1}

%  grey prop 1
% not q_{r+1}
\begin{scope}
\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
\draw[light-gray,propagator,seconddash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
\end{scope}

\begin{scope}
\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
\draw[light-gray,propagator,firstdash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
\end{scope}
\begin{scope}
\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
\draw[light-gray,propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
\end{scope}
% grey prop 1 ends here

% grey prop 2
% this is q_{r+1}
\begin{scope}
\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.45cm];
\draw[propagator,seconddash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
\end{scope}

\begin{scope}
\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.4cm];
\draw[propagator,firstdash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
\end{scope}

\begin{scope}
\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.3cm];
\draw[light-gray,propagator] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
\end{scope}

% grey prop 2 ends here

\end{scope}

\node at (90:\radius*0.15 cm) {\tiny $q_r$};
\node at (\angle*7.5:\radius*0.83) {\tiny $p_{r+1}$};
\node[light-gray] at (\angle*11:\radius*0.75 cm) {\tiny $q_{r+1}$};

\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
\node at (12*\angle:\radius*1.1) {\tiny $j_r$};

% overall circle
\begin{scope}
\clip (-\radius*1.1,0.7) rectangle (\radius*1.1,\radius*1.1);
\draw[-] (0,0) circle[radius=\radius cm];
\end{scope}

\end{scope} % ends overall clip
\end{tikzpicture}

\end{tabular}
\]
In each case, the diagram indicates how to choose $q_{r+1}$ satisfying the induction hypothesis.  In the third case, note that \textit{both} ends of $p_{r+1}$ must share their edge with a propagator of length $\geq 4$; the non-crossing hypothesis on propagators guarantees that at least one will bound a region not containing $p_{r+1}$.
\end{proof}

>>>>

\note{Are the next few definitions used outside the proof of Lemma~\ref{lem sian 1}?  If not, then perhaps they could go inside the proof so as not to clutter the document with temporary definitions?}
\begin{dfn}
Define the restriction of $W$ to a region $[i,j]$ to be the subdiagram obtained by forgetting all propagators not wholly supported on vertices in the cyclic interval $[i,j]$.  Denote this diagram by $W_{[i,j]}$.
\end{dfn}
\note{I think there's an issue here about what we mean by subdiagram; in def 1.5 we say a subdiagram is of the form $(P, V(P))$ which is certainly not what we want here; in fact I think we want the subdiagram where the vertex set is unchanged and only the propagator set is restricted (the other possibility would be to restrict the vertex set to $[i, j]$, but then the lengths of propagators can change and in the way we want to use it (see paragraph below) $p$ will become very non-admissible).  I think def 1.5 should be removed and we should say that for a WLD $(P, V)$ subdiagrams are any $(P', V')$ with $P'\subseteq P$, $V'\subseteq V$ and all supporting vertices of elements of $P'$ in $V'$; this seems to me to be the natural notion of subobject.}

@@

\begin{lem}\label{lem sian 1}
  Let $W$ be an admissible WLD in which each vertex supports at least one propagator.  Then exactly one of the following two things occurs.
  \begin{enumerate}
    \item $W$ has a propagator of length 3 with a propagator of length 2 inside it.
    \item $W$ admits no propagators of length 3, and one or more of the following things occurs.
      \begin{enumerate}
        \item There is a propagator of length $2$, say $(i, i+1, i+2, i+3)$ such that no other propagators ends on either the edge $(i, i+1)$ or the edge $(i+2, i+3)$.\label{item lonely 2}
        \item There exists a pair of propagators of length $2$ with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(j, j+1, j+2, j+3)$, no other propagator ends between $i+2$ and $j+1$, and $j\in\{i+2, i+3, i+4\}$.\label{item pair of 2s}
        \item There exists a propagator of length exactly 4 with only a propagator of length 2 inside it.\label{item 4 and 2}
      \end{enumerate}
  \end{enumerate}
\end{lem}

\begin{proof}
  Suppose first that $W$ has a propagator of length $3$, $p=(i, i+1, i+3, i+4)$.  By Remark~\ref{rem:props of length 2 and 3} along with the fact that every vertex of $W$ supports at least one propagator, we have that $i+2$ supports exactly one propagator and this propagator must have length 2 by noncrossingness.

@@

  We will inductively construct a sequence of pairs of propagators $(p_r,q_r)$ satisfying: $\ell(p_r) = 2$, and $p_r$ either forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2} from the statement,
  %a configuration \eqref{eq:2 prop config} in $D$
  or there is a propagator $q_r$ satisfying
\begin{itemize}
\item $\ell(q_r) \geq 4$.
\item $q_r$ bounds a region of $W$ which contains strictly fewer vertices than that bounded by $q_{r-1}$ and the restriction of $W$ to this region does not contain any of the propagators $p_1, \dots, p_r$.
\end{itemize}
Since $W$ contains finitely many vertices, this must eventually terminate in one of the three desired configurations. %a configuration of the form \eqref{eq:2 prop config}.

Start by choosing a propagator $p_1$ of length 2 in $W$ (which exists by Remark~\ref{rem:props of length 2 and 3}), and write $(j_1,j_1+1,j_1+2,j_1+3)$ for its support.  If it is part of one of the configurations we are looking for then we are done, 
%a configuration \eqref{eq:2 prop config} we are done,
so suppose otherwise: since $p_1$ is not in configuration \ref{item lonely 2} then there must be a second propagator starting either on edge $(j_1, j_1+1)$ or $(j_1+2, j_1+3)$.  Flipping the diagram if necessary, assume the former.  Since $p_1$ is not in configuration \ref{item pair of 2s} and every vertex is supported then there must exist a propagator $q_1$ of length $\geq 4$ with one end on edge $(j_1,j_1+1)$ or on edge $(j_1-1, j_1)$ or on edge $(j_1-2, j_1-1)$.  This bounds a region $[i_1,k_1]$ (where $k_1 \in \{j_1-1, j_1, j_1+1\}$) which does not contain $p_1$.

Now suppose $q_{r}$ exists by the induction hypothesis and bounds a region $[i_r,k_r]$.  Consider the restricted diagram $W_r:=W_{[i_r,k_r]}$; by the original hypotheses on $W$ every vertex $l \in [i_r+2,k_r-2]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must have support $\geq 1$, while the same is true for $l \in \{i_r,i_r+1,k_r-1,k_r\}$ because of $q_r$.

By Remark~\ref{rem:props of length 2 and 3}, $W_r$ admits at least one propagator of length 2.  $W_r$ has no propagators of length $3$ since $W$ has none. \note{now the question really is important about what length means in the restricted diagram; as written the restricted diagram has the same vertex set so length is unchanged.}   Let $p_{r+1}$ be a propagator of length 2 in $W_r$; if it forms part of configuration \ref{item lonely 2}, \ref{item pair of 2s}, or \ref{item 4 and 2}
%the configuration \eqref{eq:2 prop config}
then we are done, so assume otherwise.

Note we may replace $q_r$ by any other propagator of length $\geq 4$ in $W_r$ which contains $p_{r+1}$ while still satisfying all the hypotheses, and so, without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ which contain $p_{r+1}$.

There are two cases to consider.
The first case is that neither end of $p_{r+1}$ lies on an edge contained in the possibly empty interval $[i_r+3,k_r-3]$, then since $p_{r+1}$ has length 2, it must be that $[i_r+3,k_r-3]$ is at most a single edge, and so $q_r$ has length $\leq 6$.  Since $p_{r+1}$ has one end before $i_r+3$ and the other after $k_r-3$, the only propagators inside $q_r$ that do not also contain $p_{r+1}$ must have both ends in $[i_r, i_r+3]$ or both ends in $[k_r-3, k_r]$ and hence be of length 2.  Therefore, if $q_r$ contains a propagator $t$ of length $\leq 4$, this propagator must also contain $p_{r+1}$ which is impossible my minimality.  Therefore, if $q_r$ contains another propagator of length $2$ we would have configuration \ref{item pair of 2s} which we have already assumed does not occur.  Consequently, $q_r$ contains only $p_{r+1}$; if $q_r$ is of length $4$ then we have \ref{item 4 and 2} and if $q_r$ is of length $5$ or $6$ then we have either \ref{item lonely 2} or an unsupported vertex, all of which are impossible.  Therefore the first case cannot occur.

The second case is that at least one endpoint of $p_{r+1}$ lies on an edge contained in the interval $[i_r+3,k_r-3]$.  Up to symmetry we can write $p_{r+1} = (j_{r+1}, j_{r+1}+1, j_{r+1}+2, j_{r+1}+3)$ where $(j_{r+1}+2, j_{r+1}+3)$ is contained in $[i_r+3, k_r-3]$.  Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and vertex $j_{r+1}+4$ is supported (and not by $q_r$ since $j_{r+1}+4 \leq k_r-2$), there is some propagator $t$ with one end in $[j_{r+1}+2, j_{r+1}+4]$ and length $\geq 4$.  By noncrossingness $t$ is contained in $q_{r}$.  $t$ does not contain $p_{r+1}$ by minimality and so we may set $q_{r+1} = t$ to continue the induction.

The overall result, then follows by induction.

\note{The picture didn't apply any longer, but perhaps a new one would be nice?}
\note{Also, the way you had it set out, you never needed a minimality argument; this was essentially beacause in your third picture, you could choose the side which didn't contain $p_{r+1}$. The same argument could work here, but I was finding it was getting a bit heavy to explain it that way, and the minimality approach seemed like it was lighter.  See what you think}
%% this was 100% a productive use of my time
%
%\[\begin{tabular}{ccc}
%% possibility 1
%\begin{tikzpicture}
%\pgfmathsetmacro{\radius}{2}
%\pgfmathsetmacro{\angle}{15}
%\begin{scope}
%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
%
%% vertices 
%\foreach \i in {2,3,4,6,7,8,9,10}{
%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
%}
%
%% \dots 
%\foreach \i in {1,2,3}{
%	\node at (65 + \i*5:\radius cm) {$\cdot$};
%}
%
%\begin{scope} % this scope contains the propagators
%\clip (0,0) circle[radius=\radius];
%
%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.7:\radius*1.2 cm); % q_r
%\draw[propagator] (\angle*7.7:\radius*1.1 cm) to [bend left=90] (\angle*9.45:\radius*1.1 cm); % p_{r+1}
%
%% grey prop begins here
%
%\begin{scope}
%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.45cm];
%\draw[light-gray,propagator,seconddash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
%\end{scope}
%
%\begin{scope}
%\clip (0,0) circle[radius=\radius];
%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.4cm];
%\draw[light-gray,propagator,firstdash] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
%\end{scope}
%
%\begin{scope}
%\clip (\angle*7.5:\radius cm) circle[radius=\radius*0.3cm];
%\clip (0,0) circle[radius=\radius];
%\draw[light-gray,propagator] (\angle*6:\radius*1.02 cm) circle[x radius=\radius*0.4cm, y radius = \radius*0.3cm];
%\end{scope}
%% end gray prop
%
%\end{scope}
%
%
%\node at (90:\radius*0.30 cm) {\tiny $q_r$};
%\node at (\angle*8:\radius*0.73) {\tiny $p_{r+1}$};
%\node[light-gray] at (\angle*4.9:\radius*0.77 cm) {\tiny $q_{r+1}$};
%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
%\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
%
%
%% circle/edges; needs to happen last to overlap gray
%\begin{scope}
%\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
%\draw[-] (0,0) circle[radius=\radius cm];
%\end{scope}
%
%\end{scope} % ends the overall rectangle clipping
%\end{tikzpicture}
%
%&
%
%% possibility 2
%\begin{tikzpicture}
%\pgfmathsetmacro{\radius}{2}
%\pgfmathsetmacro{\angle}{15}
%\begin{scope}
%% overall clipping to make the size sensible
%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
%
%
%% vertices
%\foreach \i in {2,3,4,6,7,8,9,10}{
%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
%}
%
%% \dots
%\foreach \i in {1,2,3}{
%	\node at (65 + \i*5:\radius cm) {$\cdot$};
%}
%
%\begin{scope} % props
%\clip (0,0) circle[radius=\radius cm]; 
%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*9.6:\radius*1.2 cm); % q_r
%\draw[propagator] (\angle*6.7:\radius*1.1 cm) to [bend left=90] (\angle*8.6:\radius*1.1 cm); % p_{r+1}
%
%%% grey prop starts here
%
%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
%\draw[light-gray,propagator,seconddash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
%\end{scope}
%
%\begin{scope}
%\clip (0,0) circle[radius=\radius];
%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
%\draw[light-gray,propagator,firstdash] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
%\end{scope}
%
%\begin{scope}
%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
%\clip (0,0) circle[radius=\radius];
%\draw[light-gray,propagator] (\angle*4.5:\radius*1.3 cm) circle[y radius = 0.5*\radius cm,x radius=\radius*0.7cm];
%\end{scope}
%% grey prop ends here
%
%
%\node at (90:\radius*0.32 cm) {\tiny $q_r$};
%\node at (\angle*7.75:\radius*0.75) {\tiny $p_{r+1}$};
%\node[light-gray] at (\angle*4.5:\radius*0.7 cm) {\tiny $q_{r+1}$};
%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
%\node at (9*\angle:\radius*1.1) {\tiny $j_r$};
%
%% circle/edges
%\begin{scope}
%\clip (-\radius*1.1,0.9) rectangle (\radius*1.1,\radius*1.1);
%\draw[-] (0,0) circle[radius=\radius cm];
%\end{scope}
%
%\end{scope} % ends overall clip
%\end{tikzpicture}
%
%&
%
%% possiblitiy 3
%\begin{tikzpicture}
%\pgfmathsetmacro{\radius}{2}
%\pgfmathsetmacro{\angle}{12}
%\begin{scope}
%\clip (-\radius*1.1,0) rectangle (\radius*1.1,\radius*1.1);
%
%% vertices
%\foreach \i in {2,3,6,7,8,9,12,13}{
%	\draw (\angle*\i:\radius*0.98) --  (\angle*\i:\radius*1.02);
%}
%
%% \dots
%\foreach \i in {1,2,3}{
%	\node at (44 + \i*5:\radius cm) {$\cdot$};
%	\node at (116 + \i*5:\radius cm) {$\cdot$};
%}
%
%\begin{scope} % props
%\clip (0,0) circle[radius=\radius cm];
%\draw[propagator] (\angle*2.4:\radius*1.2 cm) to [bend left=30] (\angle*12.6:\radius*1.2 cm); % q_r
%\draw[propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=100] (\angle*8.5:\radius*1.05 cm); % p_{r+1}
%
%%  grey prop 1
%% not q_{r+1}
%\begin{scope}
%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.45cm];
%\draw[light-gray,propagator,seconddash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
%\end{scope}
%
%\begin{scope}
%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.4cm];
%\draw[light-gray,propagator,firstdash] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
%\end{scope}
%\begin{scope}
%\clip (\angle*6.5:\radius cm) circle[radius=\radius*0.3cm];
%\draw[light-gray,propagator] (\angle*6.5:\radius*1.1 cm) to [bend left=90] (\angle*12.5:\radius*1.1cm);
%\end{scope}
%% grey prop 1 ends here
%
%% grey prop 2
%% this is q_{r+1}
%\begin{scope}
%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.45cm];
%\draw[propagator,seconddash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
%\end{scope}
%
%\begin{scope}
%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.4cm];
%\draw[propagator,firstdash,light-gray] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
%\end{scope}
%
%\begin{scope}
%\clip (\angle*8.5:\radius cm) circle[radius=\radius*0.3cm];
%\draw[light-gray,propagator] (\angle*8.8:\radius*1.1 cm) to [bend left=90] (\angle*12:\radius*1.1cm);
%\end{scope}
%
%% grey prop 2 ends here
%
%
%
%\end{scope}
%
%\node at (90:\radius*0.15 cm) {\tiny $q_r$};
%\node at (\angle*7.5:\radius*0.83) {\tiny $p_{r+1}$};
%\node[light-gray] at (\angle*11:\radius*0.75 cm) {\tiny $q_{r+1}$};
%
%\node at (2*\angle:\radius*1.1) {\tiny $i_r$};
%\node at (12*\angle:\radius*1.1) {\tiny $j_r$};
%
%
%
%% overall circle
%\begin{scope}
%\clip (-\radius*1.1,0.7) rectangle (\radius*1.1,\radius*1.1);
%\draw[-] (0,0) circle[radius=\radius cm];
%\end{scope}
%
%
%\end{scope} % ends overall clip
%\end{tikzpicture}
%
%\end{tabular}
%\]
%In each case, the diagram indicates how to choose $q_{r+1}$ satisfying the induction hypothesis.  In the third case, note that \textit{both} ends of $p_{r+1}$ must share their edge with a propagator of length $\geq 4$; the non-crossing hypothesis on propagators guarantees that at least one will bound a region not containing $p_{r+1}$.

\begin{rmk}
In the case that all vertices of an admissible WLD $W$ support at least two propagators, then Lemma~\ref{lem sian 1} substantially simplifies.  By Remark~\ref{rem:props of length 2 and 3}, $W$ has no propagators of length $3$, so the first item of Lemma~\ref{lem sian 1} cannot occur at all.  Configurations \ref{item lonely 2} and \ref{item 4 and 2} also necessarily entail vertices with support $1$ as does configuration \ref{item pair of 2s} unless $j=i+2$.  So in the case that $W$ has all vertices with support at least two then $W$ must contain a pair of propagators of length $2$  with the property that the first propagator is $(i, i+1, i+2, i+3)$, the second is $(i+2, i+3, i+4, i+5)$ and no other propagator ends on the edge $(i+2, i+3)$.
\end{rmk}
